\LARGE \bf An Overview of Reinforcement Learning

### 2020-07-15 paper/paper.tex
Add more algorithms and references

\usepackage{todonotes}

\title{\LARGE \bf
An Overview of reinforcement learning
}

\author{Emmanuel Madrigal% <-this % stops a space
}

@@

\maketitle\todo{Fix title}

@@

\subsection{Deep Q-Learning}

@@

\subsection{Actor-Critics}

@@

\subsection{REINFORCE}

@@

\addtolength{\textheight}{-12.5cm}   % This command serves to balance the column lengths
% on the last page of the document manually. It shortens
% the textheight of the last page by a suitable amount.
% This command does not take effect until the next page
% so it should come on the page before the last. Make
% sure that you do not shorten the textheight too much.

>>>>

\usepackage{todonotes}
\def\tec{$^1$}

\title{\LARGE \bf An Overview of Reinforcement Learning}

\author{
  Emmanuel Madrigal \\
  \vspace{3pt}
  emmadrigal@estudiantec.cr
  \vspace{-18pt}
}

@@

\maketitle

@@

\subsection{Deep Q-Learning~\cite{minh_dqn}}

@@

\subsection{Actor Critic~\cite{konda2000actor}}

@@

The Actor Critic has two main variants: the Asynchronous Advantage
Actor Critic (A3C) and the Advantage Actor Critic (A2C).

A3C was introduced in ~\cite{mnih2016asynchronous}. In essence, A3C
implements parallel training where multiple workers in parallel
environments independently update a global value function—hence
``asynchronous''. One key benefit of having asynchronous actors is
effective and efficient exploration of the state space.

A2C~\cite{wu_2017} is like A3C but without the asynchronous part; this
means a single-worker variant of the A3C. It was empirically found
that A2C produces comparable performance to A3C while being more
efficient.

\subsection{Double DQN~\cite{NIPS2010_3964}}

Taking the largest q value (which is noisy) as the best action to take
can lead to false positives. If non-optimal actions are regularly
given a higher Q value than the optimal best action, the learning will
be complicated.  The solution is: when we compute the Q target; we use
two networks to decouple the action choice from the target Q value
generation.

\begin{itemize}
\item Use a DQN network to select what is the best action to take for
  the next state (the action with the highest Q value).
\item Use a target network to calculate the target Q value of taking
  that action at the next state.
\end{itemize}

\subsection{Deep Deterministic Policy Gradient~\cite{lillicrap2015continuous}}

Deep Deterministic Policy Gradient (DDPG) is an algorithm which
concurrently learns a Q-function and a policy. It uses off-policy data
and the Bellman equation to learn the Q-function, and uses the
Q-function to learn the policy.

This approach is closely connected to Q-learning, and is motivated the same way: if you know the optimal action-value function $Q^*(s,a)$, then in any given state, the optimal action $a^*(s)$ can be found by solving

$$
a^*(s) = \underset{a}{arg\ max} Q^*(s,a).
$$

DDPG interleaves learning an approximator to $Q^*(s,a)$ with learning an
approximator to $a^*(s)$, and it does so in a way which is specifically
adapted for environments with continuous action spaces.

Because the action space is continuous, the function $Q^*(s,a)$ is
presumed to be differentiable with respect to the action
argument. This allows to set up an efficient, gradient-based learning
rule for a policy $\mu(s)$ which exploits that fact. Then, instead of
running an expensive optimization subroutine each time we wish to
compute $max_a Q(s,a)$, we can approximate it with $\max_a Q(s,a)
\approx Q(s,\mu(s))$.

\subsection{SARSA~\cite{rummery1994line}}

The Sarsa algorithm is an On-Policy algorithm for reinforcement learning. The
major difference between it and Q-Learning, is that the maximum reward
for the next state is not necessarily used for updating the
Q-values. Instead, a new action, and therefore reward, is selected
using the same policy that determined the original action. The name
Sarsa actually comes from the fact that the updates are done using the
quintuple $Q(s, a, r, s', a')$. Where: $s, a$ are the original state and
action, $r$ is the reward observed in the following state and $s', a'$ are
the new state-action pair.

\subsection{Other}

Other algorithms include:

\begin{itemize}
\item Proximal Policy Optimization~\cite{schulman2017proximal}.
  \item Trust-Region Policy Optimization~\cite{schulman2015trust}.
  \item Deterministic Policy Gradient~\cite{silver2014deterministic}.
  \item Generative Adversarial Imitation Learning~\cite{ho2016generative}.
  \item Hindsight Experience Relay~\cite{AndrychowiczWRS17}.
  \item Soft Actor Critic~\cite{abs-1801-01290}.
  \item Twin Delayed DDPG~\cite{dankwa2019twin}.
  \item Trust Region Policy Optimization~\cite{schulman2015trust}.
\end{itemize}

@@

\addtolength{\textheight}{-9.5cm}   % This command serves to balance the column lengths
% on the last page of the document manually. It shortens
% the textheight of the last page by a suitable amount.
% This command does not take effect until the next page
% so it should come on the page before the last. Make
% sure that you do not shorten the textheight too much.
